Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers

### 2016-09-27 notes/paper/paper.tex
Incremental changes.

\begin{figure}[!ht]
   \centering
   \subfloat[\label{fig:multiple_comparison}]{\includegraphics[width=0.45\textwidth]{more_time_plots.png}}
   \quad
   \subfloat[\label{fig:timing_refs}]{\includegraphics[width=0.45\textwidth]{one_and_two_references.png}}
   \caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 microcontroller processor. The time window used for (b) is 4.0 seconds with timings measured at sampling frequencies of $16, 32, 62, 64, 75, 100,$ and $128$ Hz.}
   \label{fig:timing}
\end{figure}
%
Because the accelerometer was not connected to the microcontroller at the time of writing this paper, randomized data was used for the purpose of analyzing the throughput performance on the device while varying the parameters which accurately models the processing load we would expect when we do have the accelerometer connected to the microcontroller.
Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process and operating at decimation $2$.
Because the FFT dominates the processing load, and a custom FFT was written specifically for this unit and optimized for even-powered factors, one expects best throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued, non-radix 2, time-lengths and sampling frequencies. Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than that of the $50$Hz.
Figure \ref{fig:timing_refs} shows the execution time over a $4.0$ second time window at decimation $8$ while varying the sampling frequency and number of references. Because the pre-processing execution time does not change with the number of references, it's observed that matched-filtering accounts for roughly $80$\% of the processing while pre-processing accounts for the other $20$\% when processing for a single reference.
%
\begin{figure}[!ht]
   \centering
   \includegraphics[width=0.6\textwidth]{flops_graph.png}
   \caption{An estimate of the flops used to accomplish the main processing tasks. This was accomplished by tallying each of the low level operations in addition to using the $2.5 N log_2 N$ mflops estimate for real-FFTs from FFTW documentation \cite{FFTW}. Although the FFT used on the MSP432 was custom, off-line implementations of the algorithms made use of FFTW}
   \label{fig:flops_count}
\end{figure}
%
\section{Conclusion}
We have demonstrated excellent activity classification capability of the matched-filter method using data obtained from a Kinetisense tri-axis accelerometer sensor.
We have shown that real-time processing can be achieved with timing results obtained from the MSP432 microcontroller.
Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFT dominates the processing time.
We increased our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, which reduced our computational requirements.
The references used in the matched-filter are obtained from the training module where a training set is provided by the user through some specified activity and the best representative motion signature of the individual is extracted through the use of an instance-based learning algorithm.

>>>>

\begin{figure}[!ht]
   \centering
   \subfloat[\label{fig:multiple_comparison}]{\includegraphics[width=0.45\textwidth]{more_time_plots.png}}
   \quad
   \subfloat[\label{fig:timing_refs}]{\includegraphics[width=0.45\textwidth]{one_and_two_references.png}}
   \caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 microcontroller processor. The time window used for (b) is 4.0 seconds with timings measured at sampling frequencies of $16, 32, 62, 64, 75, 100,$ and $128$ Hz.}
   \label{fig:timing}
\end{figure}
%
Because the accelerometer was not connected to the microcontroller at the time of writing this paper, randomized data was used for the purpose of analyzing the throughput performance on the device while varying the parameters which accurately models the processing load we would expect when we do have the accelerometer connected to the microcontroller.
Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process and operating at decimation $2$.
Because the FFT dominates the processing load, and a custom FFT was written specifically for this unit and optimized for even-powered factors, one expects best throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued, non-radix 2, time-lengths and sampling frequencies. Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than that of the $50$Hz.
Figure \ref{fig:timing_refs} shows the execution time over a $4.0$ second time window at decimation $8$ while varying the sampling frequency and number of references. Because the pre-processing execution time does not change with the number of references, it's observed that matched-filtering accounts for roughly $80$\% of the processing while pre-processing accounts for the other $20$\% when processing for a single reference.
%
\begin{figure}[!ht]
   \centering
   \includegraphics[width=0.95\textwidth]{flops_graph.png}
   \caption{An estimate of the processing distribution based on flop counts. This estimate was obtained from the source code that was used for the performance assessment. The cost of the FFT is based on the $2.5 N log_2 N$ mflops estimate for FFTW \cite{FFTW} which was used for this performance assessment for real-FFTs. A sampling rate of $128$ Hz with the matched-filter applied over a $4$ second time window and $1.5$ seconds of reference data was used (usual standard for testing)}
   \label{fig:flops_count}
\end{figure}

An assessment of the processing costs associated with each algorithm in the process was made as seen in figure \ref{fig:flops_count}.
In addition, timing tests were done for comparison on an Intel i7-4500U 1.80 GHz processor.
Processing time came out to $12.0$ micro-seconds for dimensionality reduction processing and $114.0$ micro-seconds for matched-filter processing on the remaining two dimensions.
This proportion shows relative consistency with figure \ref{fig:flops_count} as we would expect.
FFT calls account for the bulk of the processing distribution and are part of the main processing kernel for the matched-filtering process.
%
\section{Conclusion}
We have demonstrated excellent activity classification capability of the matched-filter method using data obtained from a Kinetisense tri-axis accelerometer sensor.
We have shown that real-time processing can be achieved with timing results obtained from the MSP432 microcontroller.
Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFT dominates the processing time.
We increased our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, which reduced our computational requirements.
The references used in the matched-filter are obtained from the training module where a training set is provided by the user through some specified activity and the best representative motion signature of the individual is extracted through the use of an instance-based learning algorithm.
